On semidefinite-representable sets over valued fields

### 2025-12-10 issac2026/main.tex
commit by Simone

\documentclass[a4paper,oneside,10pt]{article}

%%%\newenvironment{proof}{\hbox{}\vspace{-0.8cm} {\bf Proof:}}{\hfill $\Box$ \vspace{0.2cm}}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color,xcolor}
%\usepackage{ulem}
\usepackage{bm}

@@

\usepackage{biblatex}
\addbibresource{../rapport/bibstage.bib}

\title{\Large \bf On semidefinite-representable sets over valued fields}

\begin{document}

\author{Corentin Cornou$^{1}$, Simone Naldi$^{2}$ and Tristan Vaccon$^{2}$}

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
%\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}

\date{Draft of \today}

\maketitle

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear and semidefinite programming, and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a valued field $K$.
  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
  of Smith normal forms.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
  semidefinite representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

%\tableofcontents

@@

\printbibliography

>>>>

\documentclass[sigconf]{acmart}

\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{amssymb} %%% ça ne fait pas compiler en acmart
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{graphicx}
\usepackage{color,xcolor}
%\usepackage{ulem}
\usepackage{bm}

@@

%\usepackage{biblatex}
%\addbibresource{../rapport/bibstage.bib}

\title{On semidefinite-representable sets over valued fields}

\author{Simone Naldi}
\affiliation{
    \institution{Université de Limoges, CNRS, XLIM}
    \city{Limoges}
    \country{France}
}

\author{Tristan Vaccon}
\affiliation{
    \institution{Université de Limoges, CNRS, XLIM}
    \city{Limoges}
    \country{France}
}

\author{Corentin Cornou}
\affiliation{
    \institution{}
    \city{}
    \country{France}
}

%\copyrightyear{2026}
%\acmYear{2026}
%\setcopyright{cc}
%\setcctype{by}
%\acmConference[ISSAC '26]{International Symposium on Symbolic and Algebraic Computation}{Date}{Place}
%\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC '26), date, place}\acmDOI{}
%\acmISBN{}

%\begin{CCSXML}
%<ccs2012>
%   <concept>
%       <concept_id>10010147.10010148.10010149.10010150</concept_id>
%       <concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
%       <concept_significance>500</concept_significance>
%       </concept>
% </ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Computing methodologies~Algebraic algorithms}

\keywords{keywords}

\begin{abstract}
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear and semidefinite programming, and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a valued field $K$.
  For $K$-polyhedra and linear programming over $K$ we give an algorithm based on computation
  of Smith normal forms.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  In particular, we showcase examples of non-polyhedral $K$-spectrahedra and of sets that are
  semidefinite representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

\begin{document}
\maketitle

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
